---
title: "Lab 8"
author: "Kiera Matiska"
date: "11/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Attach Packages
library(tidyverse)
library(modelsummary)
library(corrplot)
library(broom)
library(here)
```

### Read in slo_homes.csv

```{r}
homes <- read_csv(here("data", "slo_homes.csv"))
```

### Create a subset with 4 cities

Task: Creats a subset (called homes_subset) that only contains observations where the city is:

- "San Luis Obispo"
- "Atascadero"
- "Arroyo Grande"
- "Santa Maria-Orcutt"

```{r}
homes_subset <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Atascadero", "Arroyo Grande", "Santa Maria-Orcutt"))

# If == instead of %in%, it looks for these variable in order line by line. San Luis Obispo first, then Atascadero, then Arroyo Grande, then Santa Maria-Orcutt over and over again.
# Use unique() is console to check the variables in a certain column
```

### A little exploration

Task: using the subset you just made, create a summary table that has the mean and standard deviation of home prices grouped by city and sale status

```{r}
# Using eval = FALSE is code chuck set up, the code will not run in the background, even when include = TRUE

homes_subset %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = mean(Price),
            sd_price = sd(Price))
```

Task: explote the relationship between square footage and home price (from homes_subset) in a scatter plot

```{r}
ggplot(data = homes_subset,
       aes(x = SqFt, y = Price)) +
  geom_point() +
  geom_smooth(method = "lm")

# Linear relationship with a positive correlation between square footage and home prices
# Possible why outlier: Property size, the view, etc. 
```

### Try a few linear models

Use multiple linear regression to investigate relationships between several predictor variables and home price

Create two differment permutationd of this model:

(1) Price ~ Ctiy, Bedrooms, Bathrooms, SqFt, Status (lm1)
(2) Price ~ City, SqFt, Status (lm2)
(3) Try another one (lm3)

```{r}
# Arroyo Grande is the reference level
lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + Status, data = homes_subset)
# R^2 interpretation: Almost 54% of variance in sales price is explained by the variables in this model

lm2 <- lm(Price ~ City + SqFt + Status, data = homes_subset)

lm3 <- lm(Price ~ SqFt, data = homes_subset)

# To reorder city list and make San Luis Obispo the reference variable
new_homes_subset <- homes_subset %>% 
  mutate(City = fct_relevel(City, "San Luis Obispo"))

# This will use SLO as the reference level for city
lm_slo <- lm(Price ~ City + SqFt, data = new_homes_subset)

summary(lm_slo)
```

### Explore correlations between quantitative variables

Task: make a subset called homes_quant (starting from homes_subset) that only contains the variables from Price through SqFt

```{r}
homes_quant <- homes_subset %>% 
  select(Price:SqFt)

homes_cor <- cor(homes_quant)

corrplot(homes_cor, method = "ellipse")
```

### Compare AIC values

```{r}
AIC(lm1)
AIC(lm2)
# lower AIC shows a better balance
```

### Use `modelsummary()` to return multiple model outputs

```{r}
modelsummary(list(lm1, lm2, lm3))
```

### Check out diagnostic plots for lm1

```{r}
plot(lm1)
# Graph 1 and 3: homoscedasticity
# Graph 2: Looks linear, but make sure to look at coefficients
# Graph 4:
```

### Use `broom::Augment()` to return the predictions for existing observations

```{r}
home_predictions <- augment(lm1)

# Make a histogram of the residuals from this model (lm1)
ggplot(data = home_predictions,
       aes(x = .resid)) +
  geom_histogram()
```

# BRANCHES ARE AWESOME
